Compositional equivalences based on Open pNets

### 2020-05-12 2016-Weak-FH-Bisim/WeakBisim.tex
improvement big proof arund page 57

\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$):\\ 
\[P[Q]_{j_0}	\models \openrule
         {
           \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}\]
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
\begin{small}$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred\,'_2},  
				{\Post\,'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred\,''_2},  
				{\Post\,''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
\end{small}\\
such that  $\Pred_2 \iff {\Pred\,'_2}
		\land {\Pred\,''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post\,'_2}\uplus 
		{\Post\,''_2}$ where ${\Post\,''_2}$ is the restriction of $\Post_2$ over variables  $\vars(Q)$.

@@

We introduce the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):\\
$\begin{array}{l}\displaystyle{
\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_2)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
\displaystyle{
\bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}
\end{array}$

Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps. In other words, if $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.  we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ into $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$. Note that self-loops where $Q$ does an action but stays at the same state are not removed. We proceed in the same way  for states named $u$. To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
\begin{small}
$\forall p\! \in\! [0..n_1]~ Q\models{\openrule
			{
				(\beta_{1pj}')^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{1p}}},  
				{{\Post\,''_{1p}}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,~~$  
$ Q\models{\openrule
			{
				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred\,''_2},  
				{\Post\,''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and \\
$\forall p \in [0..n_2]~ Q\models{\openrule
			{
				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{3p}}},  
				{{\Post\,''_{3p}}}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$.

@@

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_p}},  
				{{\Post\,''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$. Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$, we have:
\begin{equation*}
\begin{split}
(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{1j}}
= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
&\iff\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
\end{split}
\end{equation*}
We can obtain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$. Note that the substitutions are however more complex in the other cases. 
Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
\begin{equation}\label{eqproofbeta}
\Pred_\beta \iff \gamma_{j_0}=
\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
\end{equation}

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (they are $\tau$ transitions). By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many non-observable ($\tau$) ones.

@@

 We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$. For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$. We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
\begin{small}
$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)]~ Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,\quad
Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
				{{\Post\,''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
and\\
\begin{small}
$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{kl}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
With:
{\small
\begin{align*}
\forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
\alpha_k'=&\alpha_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
&\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
\\
\Post_k= &\bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
\end{align*}
}

@@

\noindent By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
%In this case, the number of weak open transitions
%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
Consequently,  we have:
\[\alpha_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
\alpha_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k'\displaystyle{\subst{\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = 
\alpha_k'\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
With~\ref{eqproofbeta}, we now have (the actions $\alpha'_p$ correspond to the observable actions, $\alpha_k$): 
\begin{eqnarray*}
\Pred_\beta &\iff& \gamma_{j_0}=
\mybigdotcup_{p=0}^{p=n_1+n_2+2}
\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
%&\iff&\gamma_{j_0}=
%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
%&\iff& \gamma_{j_0}=
%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
&\iff& \gamma_{j_0}=
[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
\end{eqnarray*}

@@

		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}\]

@@

		\land {\Pred\,''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\

@@

		\land {\Pred\,''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\

@@

(\gamma_{j_0}=[\alpha'_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])

@@

which is exactly what is needed.

@@

&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}\qedhere

@@

>>>>

\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$):\\ 
\[P[Q]_{j_0}	\models \openrule
         {
           \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}\]
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
\begin{small}$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred\,'_2},  
				{\Post\,'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred\,''_2},  
				{\Post\,''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{20}}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
\end{small}\\
such that  $\Pred_2 \iff {\Pred\,'_2}
		\land {\Pred\,''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post\,'_2}\uplus 
		{\Post\,''_2}$ where ${\Post\,''_2}$ is the restriction of $\Post_2$ over variables  $\vars(Q)$.

@@

We introduce the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):\\
$\begin{array}{l}\displaystyle{
\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_{20})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
\displaystyle{
\bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}
\end{array}$

Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps. In other words, if $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.  we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ into $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$. Note that self-loops where $Q$ does an action but stays at the same state are not removed. We proceed in the same way  for states named $u$. To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
\begin{small}
$\forall p\! \in\! [0..n_1]~ Q\models{\openrule
			{
				(\beta_{1pj}')^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{1p}}},  
				{{\Post\,''_{1p}}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,~~$  
$ Q\models{\openrule
			{
				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred\,''_2},  
				{\Post\,''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{20}}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and \\
$\forall p \in [0..n_2]~ Q\models{\openrule
			{
				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{3p}}},  
				{{\Post\,''_{3p}}}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$.

@@

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_p}},  
				{{\Post\,''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha'_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$. Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha'_k$ only variables of $Q$, we have:
\begin{equation*}
\begin{split}
(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{1j}}
= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
&\iff\alpha'_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
\end{split}
\end{equation*}
We can obtain similar equations for $\alpha'_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha'_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$. Note that the substitutions are however more complex in the other cases. 
Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
\begin{equation}\label{eqproofbeta}
\Pred_\beta \iff \gamma_{j_0}=
\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
\end{equation}

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha'_p$ some of them may be non-observable (they are $\tau$ transitions). By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.

@@

 We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$. For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$. We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
\begin{small}
$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)]~ Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,\quad
Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
				{{\Post\,''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha'_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
and\\
\begin{small}
$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{(v_{kl}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
With:
{\small
\begin{align*}
\forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
\alpha_k=&\alpha'_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
&\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
\\
\Post_k= &\bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
\end{align*}
}

@@

\noindent By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
%In this case, the number of weak open transitions
%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
Consequently,  we have:
\[\alpha'_{n_k}{\subst{\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
\alpha'_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k\displaystyle{\subst{\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = 
\alpha_k\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
With~\ref{eqproofbeta}, we now have. Recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable: 
\begin{eqnarray*}
\Pred_\beta &\iff& \gamma_{j_0}=
\mybigdotcup_{p=0}^{p=n_1+n_2+2}
\vis{\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
%&\iff&\gamma_{j_0}=
%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
%&\iff& \gamma_{j_0}=
%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
&\iff& \gamma_{j_0}=
[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
\end{eqnarray*}

@@

		\land \!\!\bigwedge_{p=0}^n\Big((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) \Big)}\]

@@

		\land {\Pred\,''_{2}}\land \alpha_{20}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\

@@

		\land {\Pred\,''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{20}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\

@@

(\gamma_{j_0}=[\alpha_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])

@@

which is exactly what is needed with $\gamma_{j_0}=[\beta_0..\beta_n]$.

@@

&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}

@@

Which concludes because we have we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
